A multiverse analysis of the associations between internet use and well-being

### 2023-11-13 ms.Rmd
Update renv

---
title: 'A multiverse analysis of the associations between internet use and well-being'
shorttitle: Internet and well-being
leftheader: Internet and well-being
author: 
  - name: Matti Vuorre
    affiliation: "1,2"
    corresponding: yes
    address: Tilburg University
    email: m.j.vuorre@tilburguniversity.edu
  - name: Andrew K. Przybylski
    affiliation: "2"
    email: andy.przybylski@oii.ox.ac.uk
affiliation:
  - id: 1
    institution: Tilburg School of Social and Behavioral Sciences, Tilburg University
  - id: 2
    institution: Oxford Internet Institute, University of Oxford
authornote: |
  \noindent \textbf{This manuscript is not yet peer-reviewed. The preprint is available at https://psyarxiv.com/jp5nd/}
  We used the proprietary Gallup World Poll dataset, which is available to subscribing institutions through the Gallup website. All our code and a simulated GWP dataset is available at https://doi.org/10.5281/zenodo.7774923. We did not pre-specify the sample sizes, but instead used all the available data in the Gallup database (with the exclusions detailed below). This study was not pre-registered.
keywords: well-being, internet technology, technology effects
wordcount: '`r scales::number(wordcountaddin:::word_count("ms.Rmd"), big.mark = ",")`'
bibliography: references.bib
floatsintext: yes
linenumbers: no
draft: no
mask: no
figurelist: no
tablelist: no
footnotelist: no
documentclass: apa7
classoption: doc
header-includes:
  - |
    \setlength{\parskip}{0pt}
    \setlength\parindent{24pt}
output: 
  papaja::apa6_pdf:
    number_sections: false
    keep_tex: false
  papaja::apa6_docx: 
    number_sections: false
    keep_tex: false
---

```{r}
#| label: setup
#| include: false
library(papaja)
library(scales)
library(knitr)
library(lme4)
library(ggh4x)
library(emmeans)
library(ggside)
library(ggbeeswarm)
library(broom.mixed)
library(patchwork)
library(ggdist)
library(corrr)
library(tidyverse)
library(ragg)
opts_chunk$set(
  include = FALSE,
  cache = TRUE,
  dev = "ragg_png"
)

# Parallel computation options
MAX_CORES <- as.numeric(Sys.getenv("MAX_CORES"))
if (is.na(MAX_CORES)) MAX_CORES <- parallel::detectCores(logical = FALSE)
CORES <- MAX_CORES - 2
theme_set(
  theme_linedraw(base_size = 9.6) +
    theme(
      strip.background = element_rect(fill = "gray90", color = "gray90"),
      strip.text = element_text(color = "black", hjust = 0),
      panel.grid = element_blank()
    )
)

@@

```{r}
#| label: data-clean
path <- "data-raw/gwp.rds"
if (dir.exists("data-raw/gallup") & !file.exists(path)) {

>>>>

---
title: 'A multiverse analysis of the associations between internet use and well-being'
shorttitle: Internet and well-being
leftheader: Internet and well-being
author: 
  - name: Matti Vuorre
    affiliation: "1,2"
    corresponding: yes
    address: Tilburg University
    email: m.j.vuorre@tilburguniversity.edu
  - name: Andrew K. Przybylski
    affiliation: "2"
    email: andy.przybylski@oii.ox.ac.uk
affiliation:
  - id: 1
    institution: Tilburg School of Social and Behavioral Sciences, Tilburg University
  - id: 2
    institution: Oxford Internet Institute, University of Oxford
authornote: |
  \noindent \textbf{This manuscript is not yet peer-reviewed. The preprint is available at https://psyarxiv.com/jp5nd/}
  We used the proprietary Gallup World Poll dataset, which is available to subscribing institutions through the Gallup website. All our code and a simulated GWP dataset is available at https://doi.org/10.5281/zenodo.7774923. We did not pre-specify the sample sizes, but instead used all the available data in the Gallup database (with the exclusions detailed below). This study was not pre-registered.
keywords: well-being, internet technology, technology effects
wordcount: "4,217"
bibliography: references.bib
floatsintext: yes
linenumbers: no
draft: no
mask: no
figurelist: no
tablelist: no
footnotelist: no
documentclass: apa7
classoption: doc
header-includes:
  - |
    \setlength{\parskip}{0pt}
    \setlength\parindent{24pt}
output: 
  papaja::apa6_pdf:
    number_sections: false
    keep_tex: false
  papaja::apa6_docx: 
    number_sections: false
    keep_tex: false
---

```{r}
#| label: setup
#| include: false

library(papaja)
library(scales)
library(knitr)
library(lme4)
library(ggh4x)
library(emmeans)
library(ggside)
library(ggbeeswarm)
library(broom.mixed)
library(patchwork)
library(ggdist)
library(corrr)
library(tidyverse)
opts_chunk$set(
  include = FALSE,
  cache = TRUE
)

# Parallel computation options
MAX_CORES <- as.numeric(
  Sys.getenv(
    "MAX_CORES", 
    unset = parallel::detectCores(logical = FALSE)
  )
)
CORES <- MAX_CORES - 2
theme_set(
  theme_linedraw(base_size = 9.6) +
    theme(
      strip.background = element_rect(fill = "gray90", color = "gray90"),
      strip.text = element_text(color = "black", hjust = 0),
      panel.grid = element_blank()
    )
)

@@

```{r}
#| label: data-clean

path <- "data-raw/gwp.rds"
if (dir.exists("data-raw/gallup") & !file.exists(path)) {
